Supplement for: Carbon cycling in mature and regrowth forests globally: a macroecological synthesis based on the global Forest Carbon (ForC) database

### 2021-01-25 manuscript/ERL_global_C_review.Rmd
various small fixes

schematics_caption_generic ="Arrows indicate fluxes (Mg C ha$^{-1}$ yr$^{-1}$); boxes indicate stocks (Mg C ha$^{-1}$), with variables as defined in Table 1. Presented are mean ± std, where geographically distinct areas are treated as the unit of replication. Note that variables differ in geographical representation, resulting in potential imbalances (Figs. S5-S30). Probability that estimates reflect true biome means scales with the number of distinct geographical areas represented. Dashed shape outlines indicate variables with records from <7 distinct geographic areas, and dashed arrows indicate fluxes with no data. To illustrate the magnitude of different fluxes, arrow width is proportional to the square root of the corresponding flux. An asterisk after a variable name indicates lack of C cycle closure."
TrB_mature_caption = paste( "Figure 3 | C cycle diagram for mature tropical broadleaf forests. ", schematics_caption_generic)  
TeB_mature_caption = paste( "Figure 4 | C cycle diagram for mature temperate broadleaf forests. ", schematics_caption_generic)  
TeN_mature_caption = paste( "Figure 5 | C cycle diagram for mature temperate conifer forests. ", schematics_caption_generic)  
BoN_mature_caption = paste( "Figure 6 | C cycle diagram for mature boreaal conifer forests. ", schematics_caption_generic)

@@

```{r eval = generate_figures, echo=FALSE, fig.align = "center", fig.cap = "Figure 7 | Age trends and biome differences in some of the major C fluxes: (a) $GPP$, (b) $NPP$, (c) $ANPP$, (d) $R_{soil}$, (e) $R_{eco}$, and (f) $NEP$. In each panel, the left scatterplot shows age trends in forests up to 100 years old, as characterized by a linear mixed effects model with fixed effects of age and biome. The fitted line indicates the effect of age on flux (solid lines: significant at p<0.05, dashed lines: non-significant), and non-parallel lines indicate a significant age x biome interaction. The boxplot illustrates distribution across mature forests, with different letters indicating significant differences between biomes. Data from biomes that did not meet the sample size criteria (see Methods) are plotted, but lack regression lines (young forests) or test of differences across biomes (mature forests). Individual figures for each flux with sufficient data, along with maps showing geographic distribution of the data, are given in the Supplement (Figs. S4-S19).", out.width='100%', fig.pos='H'}

@@

```{r eval = generate_figures, echo=FALSE, fig.align = "center", fig.cap = "Figure 8 | Age trends and biome differences in some of the major forest C stocks: (a) aboveground biomass, (b) foliage, (c) fine roots, (d) dead wood. In each panel, the left scatterplot  shows age trends in forests up to 100 years old, as characterized by a linear mixed effects model with fixed effects of age and biome. The fitted line indicates the effect of age on flux (solid lines: significant at p<0.05, dashed lines: non-significant), and non-parallel lines indicate a significant age x biome interaction. The boxplot illustrates distribution across mature forests, with different letters indicating signifant differences between biomes. Data from biomes that did not meet the sample size criteria (see Methods) are plotted, but lack regression lines (young forests) or test of differences across biomes (mature forests). Individual figures for each stock with sufficient data, along with maps showing geographic distribution of the data, are given in the Supplement (Figs. S20-S30).", out.width='100%', fig.pos='H'}

@@

First, improved representation of forest C cycling in models is essential to improving predictions of the future course of climate change, for the simple reason that by definition future projections extend our existing observations and understanding to conditions that do not currently exist on Earth [@mcdowell_predicting_2018; @bonan_climate_2018; @gustafson_extrapolating_2018]. 
To ensure that models are giving the right answers for the right reasons [@sulman_multiple_2018], it is important to benchmark against multiple components of the C cycle that are internally consistent with each other [@collier_international_2018; @wang_golum-cnp_2018]. 
*ForC*’s tens of thousands of records are readily available in a standardized format, and our analyses here indicate that their internal consistency is reasonably high. Integration of *ForC* with models will be valuable to improving the accuracy and reliability of models [@fer_beyond_2021].

>>>>

schematics_caption_generic ="Arrows indicate fluxes (Mg C ha$^{-1}$ yr$^{-1}$); boxes indicate stocks (Mg C ha$^{-1}$), with variables as defined in Table 1. Presented are mean ± std, where geographically distinct areas are treated as the unit of replication. Dashed shape outlines indicate variables with records from <7 distinct geographic areas, and dashed arrows indicate fluxes with no data. To illustrate the magnitude of different fluxes, arrow width is proportional to the square root of the corresponding flux. Mean component fluxes do not necessarily add up to the mean total fluxes because different sets of sites are included depending on availability of data (Figs. S5-S30). An asterisk after a variable name indicates lack of C cycle closure."
TrB_mature_caption = paste( "Figure 3 | C cycle diagram for mature tropical broadleaf forests. ", schematics_caption_generic)  
TeB_mature_caption = paste( "Figure 4 | C cycle diagram for mature temperate broadleaf forests. ", schematics_caption_generic)  
TeN_mature_caption = paste( "Figure 5 | C cycle diagram for mature temperate conifer forests. ", schematics_caption_generic)  
BoN_mature_caption = paste( "Figure 6 | C cycle diagram for mature boreaal conifer forests. ", schematics_caption_generic)

@@

```{r eval = generate_figures, echo=FALSE, fig.align = "center", fig.cap = "Figure 7 | Age trends and biome differences in some of the major C fluxes: (a) $GPP$, (b) $NPP$, (c) $ANPP$, (d) $R_{soil}$, (e) $R_{eco}$, and (f) $NEP$. In each panel, the left scatterplot shows age trends in forests up to 100 years old, as characterized by a linear mixed effects model with fixed effects of log10(age) and biome. The fitted line indicates the effect of age (solid lines: significant at p<0.05, dashed lines: non-significant), and non-parallel lines indicate a significant log10(age) x biome interaction. The boxplot illustrates distribution across mature forests, with different letters indicating significant differences between biomes. Data from biomes that did not meet the sample size criteria (see Methods) are plotted, but lack regression lines (young forests) or test of differences across biomes (mature forests). Individual figures for each flux with sufficient data, along with maps showing geographic distribution of the data, are given in the Supplement (Figs. S4-S19).", out.width='100%', fig.pos='H'}

@@

```{r eval = generate_figures, echo=FALSE, fig.align = "center", fig.cap = "Figure 8 | Age trends and biome differences in some of the major forest C stocks: (a) aboveground biomass, (b) foliage, (c) fine roots, (d) dead wood. In each panel, the left scatterplot shows age trends in forests up to 100 years old, as characterized by a linear mixed effects model with fixed effects of log10(age) and biome. The fitted line indicates the effect of age (solid lines: significant at p<0.05, dashed lines: non-significant), and non-parallel lines indicate a significant log10(age) x biome interaction. The boxplot illustrates distribution across mature forests, with different letters indicating signifant differences between biomes. Data from biomes that did not meet the sample size criteria (see Methods) are plotted, but lack regression lines (young forests) or test of differences across biomes (mature forests). Individual figures for each stock with sufficient data, along with maps showing geographic distribution of the data, are given in the Supplement (Figs. S20-S30).", out.width='100%', fig.pos='H'}

@@

First, improved representation of forest C cycling in models is essential to improving predictions of the future course of climate change, for the simple reason that by definition future projections extend our existing observations and understanding to conditions that do not currently exist on Earth [@mcdowell_predicting_2018; @bonan_climate_2018; @gustafson_extrapolating_2018]. 
To ensure that models are giving the right answers for the right reasons [@sulman_multiple_2018], it is important to benchmark against multiple components of the C cycle that are internally consistent with each other [@collier_international_2018; @wang_golum-cnp_2018]. 
*ForC*’s tens of thousands of records are readily available in a standardized format, along with all code used in the analyses presented here, and we recommend that researchers use these resources to identify and summarize data specific the analysis at hand. 
Integration of *ForC* with models will be valuable to improving the accuracy and reliability of models [@fer_beyond_2021].
